---
title: "Bumpus"
author: "Angela JACINTO"
date: "2023-09-22"
output: html_document
---

```{r setup, include=FALSE}
setwd("/Users/angelajacinto/Desktop/STAT2402/assignment2")
df <- read.table(file="/Users/angelajacinto/Desktop/STAT2402/assignment2/bumpus.txt", header=TRUE)
```

```{r}
library(ggplot2)
library(gridExtra)
library(GGally)
library(MASS)
library(broom)
library(knitr)
```

```{r}
bump <- df
# Convert 'Sex' to numeric: 1 for female, 0 for male
bump$Sex <- ifelse(bump$Sex == "f", 1, 0)
# Convert 'Survival'variable to numeric type
bump$Survival <- as.numeric(bump$Survival)
summary(bump)

bump_standard_deviations <- sapply(bump, function(x) round(sd(x, na.rm = TRUE), 4))
print(bump_standard_deviations)

str(bump)
```

Initialization
```{r}
null_model <- glm(Survival ~ 1, data = bump, family = binomial(link = logit))

candidate_predictors <- c("Sex", "TotalLength", "AlarExtent", "Weight", "BeakHead", "Humerus", "Femur", "Tibiotarsus", "SkullWidth", "Sternum")

# Initialize current model 
currentmodel <- null_model
```

Forward Selection Loop for Main Effects
```{r}
while (length(candidate_predictors) > 0) {
  # Store AIC values and models for each candidate predictor
  aic_values <- numeric(length(candidate_predictors))
  models <- list()
  
for (i in seq_along(candidate_predictors)) {
model_string <- paste("Survival ~", paste(c(attr(currentmodel$terms, "term.labels"), candidate_predictors[i]), collapse = " + "))
    
    # Fit the model
    candidate_model <- glm(as.formula(model_string), data = bump, family = binomial(link = logit))
    
    # Store the AIC value and the model
    aic_values[i] <- AIC(candidate_model)
    models[[i]] <- candidate_model
  }
  
  # Find the predictor with the smallest AIC value
  min_index <- which.min(aic_values)
  
  # Check if the AIC value is smaller than the AIC value of the current model
  if (aic_values[min_index] < AIC(currentmodel)) {
    # Update the current model to the model with the added predictor
    currentmodel <- models[[min_index]]
    
    # Remove the added predictor from the list of candidate predictors
    candidate_predictors <- setdiff(candidate_predictors, names(aic_values)[min_index])
  } else {
    break  # Exit the loop if no improvement in AIC is observed
  }
}

summary(currentmodel)
```

```{r}
# Defining predictors 
predictors <- c("TotalLength", "Humerus", "Weight", "Sternum", "BeakHead")

# Creating plot for predictor
create_plot <- function(predictor) {
  # Create a sequence for the predictor
  predictor_seq <- seq(min(bump[[predictor]]), max(bump[[predictor]]), length.out = 100)

  # Creating new data frames for prediction
  newdata_male <- data.frame(
    TotalLength = rep(mean(bump$TotalLength), 100),
    Humerus = rep(mean(bump$Humerus), 100),
    Weight = rep(mean(bump$Weight), 100),
    Sternum = rep(mean(bump$Sternum), 100),
    BeakHead = rep(mean(bump$BeakHead), 100),
    Sex = rep(0, 100)  # Male
  )

  newdata_female <- newdata_male
  newdata_female$Sex <- rep(1, 100)  # Female

  # Updating the predictor of interest
  newdata_male[[predictor]] <- predictor_seq
  newdata_female[[predictor]] <- predictor_seq

  # Generating predicted values for the new data frames
  predicted_probs_male <- predict(currentmodel, newdata=newdata_male, type="response")
  predicted_probs_female <- predict(currentmodel, newdata=newdata_female, type="response")

  # Plotting
  p <- ggplot(bump, aes_string(x=predictor, y="Survival", color = "factor(Sex)")) +
    geom_point(pch=16) +
    geom_line(data=newdata_male, aes_string(x=predictor, y=predicted_probs_male), color="black") +
    geom_line(data=newdata_female, aes_string(x=predictor, y=predicted_probs_female), color="red") +
    scale_color_manual(name = "", values=c("red", "black"), labels=c("Female", "Male")) +
    labs(title=paste(predictor, "vs Survival"), x=predictor, y="Probability of Survival") +
    theme_minimal()

  return(p)
}

# Generating and storing plots 
plots <- lapply(predictors, create_plot)

plots
```
The plot visualizes how the probability of survival changes with different predictors between genders. For each predictor, the plots display how changes in that specific variable influence the likelihood of survival, while all other factors are held constant at their mean values.

Confusion Matrix 
```{r}
library(caret)
predicted_probs <- predict(currentmodel, type = "response")
threshold <- 0.5 
predicted_class <- ifelse(predicted_probs > threshold, "Survived", "Not_Survived")
# Actual outcome of Survival
actual_class <- ifelse(bump$Survival == 1, "Survived", "Not_Survived")

# Factorize predicted and actual classes as they are character and numerical vectors
predicted_class <- factor(predicted_class, levels = c("Not_Survived", "Survived"))
actual_class <- factor(actual_class, levels = c("Not_Survived", "Survived"))

conf_mtrx <- confusionMatrix(predicted_class, actual_class)
conf_mtrx
```
Overall, these statistics indicate that the model has a fairly good predictive performance, with reasonable balance between identifying survival and non-survival cases in sparrows. The model's accuracy, sensitivity, and specificity are all moderately high, suggesting it's effectively distinguishing between the two classes.

Model Assessment: Pearson Residuals 
```{r}
bump$Pears <- residuals(currentmodel, "pearson")
bump$Fitted <- fitted(currentmodel)
with(bump, cbind(Fitted, Pears))
```

Pearson Residual vs fitted values plot
```{r}
# Create the ggplot
p_pearson <- ggplot(bump, aes(x=Fitted, y=Pears)) +
  geom_point(pch=16) + 
  geom_hline(yintercept=0, linetype="dashed") +
  labs(title="Pearson Residuals vs Fitted Values", 
       x="Fitted Values", 
       y="Pearson Residuals") 

p_pearson
```
The Pearson residuals plot is utilized to evaluate the fit of the generalized linear model. There is an uneven spread of residuals—an evidence of heteroscedasticity. This tells us that the model's precision varies across the fitted values. The plot also shows a clear pattern of the residuals with points forming a funnel shape as the fitted values increase, which suggests that the model is not capturing the relationship between the dependent and independent variables. Furthermore, there are a few points with high residuals on the positive side above 2, which suggest outliers  affecting the fit of the model.

Manual Forward Selection for main effects
```{r}
# Sex
model_with_sex <- glm(Survival ~ Sex, data = bump, family = binomial(link = logit))
aic_with_sex <- AIC(model_with_sex)

# Compare AIC Values
aic_null_model <- AIC(null_model)
print(paste("AIC with Sex:", aic_with_sex))
print(paste("AIC of Null Model:", aic_null_model))

# Decide 
if (aic_with_sex < aic_null_model) {
  m2 <- model_with_sex
  candidate_predictors <- setdiff(candidate_predictors, "Sex")
  print("Sex is included in the model.")
} else {
  print("Sex is not included in the model.")
}
```

```{r}
# Sex, Total Length 
model_with_sex_totalLength <- glm(Survival ~ Sex + TotalLength, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength <- AIC(model_with_sex_totalLength)

# Compare AIC Values
aic_m2 <- AIC(m2)
print(paste("AIC with Sex + TotalLength:", aic_with_sex_totalLength))
print(paste("AIC of Current Model (with Sex):", aic_m2))


# Decide 
if (aic_with_sex_totalLength < aic_m2) {
  m2 <- model_with_sex_totalLength
  candidate_predictors <- setdiff(candidate_predictors, "TotalLength")
  print("TotalLength is included in the model.")
} else {
  print("TotalLength is not included in the model.")
}
```

```{r}
# Sex, Total Length, AlarExtent 
model_with_sex_totalLength_alarExtent <- glm(Survival ~ Sex + TotalLength + AlarExtent, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent <- AIC(model_with_sex_totalLength_alarExtent)


# Compare AIC Values
aic_m2 <- AIC(m2)
print(paste("AIC with Sex + TotalLength + AlarExtent:", aic_with_sex_totalLength_alarExtent))
print(paste("AIC of Current Model (with Sex + TotalLength):", aic_m2))


# Decide 
if (aic_with_sex_totalLength_alarExtent < aic_m2) {
  m2 <- model_with_sex_totalLength_alarExtent
  candidate_predictors <- setdiff(candidate_predictors, "AlarExtent")
  print("AlarExtent is included in the model.")
} else {
  print("AlarExtent is not included in the model.")
}

```

```{r}
# Sex, Total Length, AlarExtent, Weight 
model_with_sex_totalLength_alarExtent_weight <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight <- AIC(model_with_sex_totalLength_alarExtent_weight)

# Compare AIC Values
aic_m2 <- AIC(m2)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight:", aic_with_sex_totalLength_alarExtent_weight))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent):", aic_m2))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight < aic_m2) {
  m2 <- model_with_sex_totalLength_alarExtent_weight
  candidate_predictors <- setdiff(candidate_predictors, "Weight")
  print("Weight is included in the model.")
} else {
  print("Weight is not included in the model.")
}

```

```{r}
# Sex, Total Length, AlarExtent, Weight, BeakHead
model_with_sex_totalLength_alarExtent_weight_beakHead <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead)

# Compare AIC Values
aic_m2 <- AIC(m2)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead:", aic_with_sex_totalLength_alarExtent_weight_beakHead))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent + Weight):", aic_m2))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead < aic_m2) {
  current_model <- model_with_sex_totalLength_alarExtent_weight_beakHead
  candidate_predictors <- setdiff(candidate_predictors, "BeakHead")
  print("BeakHead is included in the model.")
} else {
  print("BeakHead is not included in the model.")
}


```
```{r}
# Sex, Total Length, AlarExtent, Weight, BeakHead, Humerus 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus)

# Compare AIC Values
aic_m2 <- AIC(m2)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent + Weight + BeakHead):", aic_m2))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus < aic_m2) {
  m2 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus
  candidate_predictors <- setdiff(candidate_predictors, "Humerus")
  print("Humerus is included in the model.")
} else {
  print("Humerus is not included in the model.")
}
```
```{r}
# Sex, Total Length, AlarExtent, Weight, BeakHead, Humerus, Femur 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_femur <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Femur, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_femur <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_femur)

# Compare AIC Values
aic_m2 <- AIC(m2)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Femur:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_femur))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus):", aic_m2))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_femur < aic_m2) {
  m2 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_femur
  candidate_predictors <- setdiff(candidate_predictors, "Femur")
  print("Femur is included in the model.")
} else {
  print("Femur is not included in the model.")
}
```
```{r}
# Sex, Total Length, AlarExtent, Weight, BeakHead, Humerus, Tibiotarsus 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_tibiotarsus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Tibiotarsus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_tibiotarsus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_tibiotarsus)

# Compare AIC Values
aic_m2 <- AIC(m2)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Tibiotarsus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_tibiotarsus))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus):", aic_m2))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_tibiotarsus < aic_m2) {
  m2 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_tibiotarsus
  candidate_predictors <- setdiff(candidate_predictors, "Tibiotarsus")
  print("Tibiotarsus is included in the model.")
} else {
  print("Tibiotarsus is not included in the model.")
}
```
```{r}
# Sex, Total Length, AlarExtent, Weight, BeakHead, Humerus, SkullWidth
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_skullWidth <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + SkullWidth, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_skullWidth <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_skullWidth)

# Compare AIC Values
aic_m2 <- AIC(m2)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + SkullWidth:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_skullWidth))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus):", aic_m2))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_skullWidth < aic_m2) {
  m2 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_skullWidth
  candidate_predictors <- setdiff(candidate_predictors, "SkullWidth")
  print("SkullWidth is included in the model.")
} else {
  print("SkullWidth is not included in the model.")
}
```
```{r}
# Sex, Total Length, AlarExtent, Weight, BeakHead, Humerus, Sternum 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum)

# Compare AIC Values
aic_m2 <- AIC(m2)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus):", aic_m2))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum < aic_m2) {
  m2 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum
  candidate_predictors <- setdiff(candidate_predictors, "Sternum")
  print("Sternum is included in the model.")
} else {
  print("Sternum is not included in the model.")
}
```
```{r}
summary(m2)
```
The AIC of `currentmodel` (145.57) using the StepAIC procedure is better than the AIC of `m2` (147.3) using manual selection. 

Manual forward Selection for Main effects and interaction terms 
```{r}
null_model <- glm(Survival ~ 1, data = bump, family = binomial(link = logit))
# Defining Main Effects and Interaction Terms
main_effects <- c("Sex", "TotalLength", "AlarExtent", "Weight", "BeakHead", "Humerus", "Femur", "Tibiotarsus", "SkullWidth", "Sternum")
interaction_terms <- c()

for (i in main_effects) {
  for (j in setdiff(main_effects, i)) {
    interaction_terms <- c(interaction_terms, paste(i, j, sep = ":"))
  }
}
all_terms <- c(main_effects, interaction_terms)

m3 <- null_model
```

```{r}
# Sex
model_with_sex <- glm(Survival ~ Sex, data = bump, family = binomial(link = logit))
aic_with_sex <- AIC(model_with_sex)

# Compare AIC Values
aic_null_model <- AIC(null_model)
print(paste("AIC with Sex:", aic_with_sex))
print(paste("AIC of Null Model:", aic_null_model))

# Decide 
if (aic_with_sex < aic_null_model) {
  m3 <- model_with_sex
  all_terms <- setdiff(all_terms, "Sex")
  print("Sex is included in the model.")
} else {
  print("Sex is not included in the model.")
}

```
```{r}
# Sex, TotalLength
model_with_sex_totalLength <- glm(Survival ~ Sex + TotalLength, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength <- AIC(model_with_sex_totalLength)


# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength:", aic_with_sex_totalLength))
print(paste("AIC of Current Model (with Sex):", aic_m3))


# Decide 
if (aic_with_sex_totalLength < aic_m3) {
  m3 <- model_with_sex_totalLength
  all_terms <- setdiff(all_terms, "TotalLength")
  print("TotalLength is included in the model.")
} else {
  print("TotalLength is not included in the model.")
}
```

```{r}
# Sex, TotalLength, AlarExtent
model_with_sex_totalLength_alarExtent <- glm(Survival ~ Sex + TotalLength + AlarExtent, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent <- AIC(model_with_sex_totalLength_alarExtent)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent:", aic_with_sex_totalLength_alarExtent))
print(paste("AIC of Current Model (with Sex + TotalLength):", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent
  all_terms <- setdiff(all_terms, "AlarExtent")
  print("AlarExtent is included in the model.")
} else {
  print("AlarExtent is not included in the model.")
}

```
```{r}
# Sex, TotalLength, AlarExtent, Weight
model_with_sex_totalLength_alarExtent_weight <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight <- AIC(model_with_sex_totalLength_alarExtent_weight)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight:", aic_with_sex_totalLength_alarExtent_weight))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent):", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight
  all_terms <- setdiff(all_terms, "Weight")
  print("Weight is included in the model.")
} else {
  print("Weight is not included in the model.")
}
```

```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead
model_with_sex_totalLength_alarExtent_weight_beakHead <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead:", aic_with_sex_totalLength_alarExtent_weight_beakHead))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent + Weight):", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead
  all_terms <- setdiff(all_terms, "BeakHead")
  print("BeakHead is included in the model.")
} else {
  print("BeakHead is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent + Weight + BeakHead):", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus
  all_terms <- setdiff(all_terms, "Humerus")
  print("Humerus is included in the model.")
} else {
  print("Humerus is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Femur
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_femur <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Femur, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_femur <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_femur)


# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Femur:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_femur))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus):", aic_m3))


# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_femur < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_femur
  all_terms <- setdiff(all_terms, "Femur")
  print("Femur is included in the model.")
} else {
  print("Femur is not included in the model.")
}

```

```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Tibiotarsus
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_tibiotarsus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Tibiotarsus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_tibiotarsus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_tibiotarsus)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Tibiotarsus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_tibiotarsus))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus):", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_tibiotarsus < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_tibiotarsus
  all_terms <- setdiff(all_terms, "Tibiotarsus")
  print("Tibiotarsus is included in the model.")
} else {
  print("Tibiotarsus is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, SkullWidth
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_skullWidth <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + SkullWidth, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_skullWidth <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_skullWidth)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + SkullWidth:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_skullWidth))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus):", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_skullWidth < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_skullWidth
  all_terms <- setdiff(all_terms, "SkullWidth")
  print("SkullWidth is included in the model.")
} else {
  print("SkullWidth is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus):", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum
  all_terms <- setdiff(all_terms, "Sternum")
  print("Sternum is included in the model.")
} else {
  print("Sternum is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength))
print(paste("AIC of Current Model (with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum):", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength
  all_terms <- setdiff(all_terms, "Sex:TotalLength")
  print("Sex:TotalLength is included in the model.")
} else {
  print("Sex:TotalLength is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent
  all_terms <- setdiff(all_terms, "Sex:AlarExtent")
  print("Sex:AlarExtent is included in the model.")
} else {
  print("Sex:AlarExtent is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Sex:Weight
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_weight <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Weight, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_weight <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_weight)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Weight:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_weight))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_weight < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_weight
  all_terms <- setdiff(all_terms, "Sex:Weight")
  print("Sex:Weight is included in the model.")
} else {
  print("Sex:Weight is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Sex:BeakHead
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_beakHead <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:BeakHead, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_beakHead <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_beakHead)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:BeakHead:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_beakHead))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_beakHead < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_beakHead
  all_terms <- setdiff(all_terms, "Sex:BeakHead")
  print("Sex:BeakHead is included in the model.")
} else {
  print("Sex:BeakHead is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Sex:Humerus
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_humerus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Humerus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_humerus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_humerus)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Humerus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_humerus))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_humerus < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_humerus
  all_terms <- setdiff(all_terms, "Sex:Humerus")
  print("Sex:Humerus is included in the model.")
} else {
  print("Sex:Humerus is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Sex:Femur
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_femur <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_femur <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_femur)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_femur))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_femur < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_femur
  all_terms <- setdiff(all_terms, "Sex:Femur")
  print("Sex:Femur is included in the model.")
} else {
  print("Sex:Femur is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Sex:Tibiotarsus
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_tibiotarsus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Tibiotarsus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_tibiotarsus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_tibiotarsus)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Tibiotarsus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_tibiotarsus))
print(paste("AIC of Current Model:", aic_m3))


# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_tibiotarsus < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_tibiotarsus
  all_terms <- setdiff(all_terms, "Sex:Tibiotarsus")
  print("Sex:Tibiotarsus is included in the model.")
} else {
  print("Sex:Tibiotarsus is not included in the model.")
}

```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Sex:SkullWidth
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_skullWidth <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:SkullWidth, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_skullWidth <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_skullWidth)


# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:SkullWidth:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_skullWidth))
print(paste("AIC of Current Model:", aic_m3))


# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_skullWidth < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_skullWidth
  all_terms <- setdiff(all_terms, "Sex:SkullWidth")
  print("Sex:SkullWidth is included in the model.")
} else {
  print("Sex:SkullWidth is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Sex:Sternum
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_sternum <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Sternum, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_sternum <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_sternum)


# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Sternum:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_sternum))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_sternum < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_sex_sternum
  all_terms <- setdiff(all_terms, "Sex:Sternum")
  print("Sex:Sternum is included in the model.")
} else {
  print("Sex:Sternum is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, TotalLength:AlarExtent
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_alarExtent <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:AlarExtent, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_alarExtent <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_alarExtent)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:AlarExtent:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_alarExtent))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_alarExtent < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_alarExtent
  all_terms <- setdiff(all_terms, "TotalLength:AlarExtent")
  print("TotalLength:AlarExtent is included in the model.")
} else {
  print("TotalLength:AlarExtent is not included in the model.")
}

```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, TotalLength:Weight
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_weight <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:Weight, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_weight <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_weight)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:Weight:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_weight))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_weight < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_weight
  all_terms <- setdiff(all_terms, "TotalLength:Weight")
  print("TotalLength:Weight is included in the model.")
} else {
  print("TotalLength:Weight is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, TotalLength:BeakHead
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_beakHead <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:BeakHead, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_beakHead <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_beakHead)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:BeakHead:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_beakHead))
print(paste("AIC of Current Model:", aic_m3))


# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_beakHead < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_beakHead
  all_terms <- setdiff(all_terms, "TotalLength:BeakHead")
  print("TotalLength:BeakHead is included in the model.")
} else {
  print("TotalLength:BeakHead is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, TotalLength:Humerus 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_humerus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:Humerus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_humerus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_humerus)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:Humerus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_humerus))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_humerus < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_humerus
  all_terms <- setdiff(all_terms, "TotalLength:Humerus")
  print("TotalLength:Humerus is included in the model.")
} else {
  print("TotalLength:Humerus is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, TotalLength:Femur
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_femur <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:Femur, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_femur <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_femur)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:Femur:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_femur))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_femur < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_femur
  all_terms <- setdiff(all_terms, "TotalLength:Femur")
  print("TotalLength:Femur is included in the model.")
} else {
  print("TotalLength:Femur is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, TotalLength:Tibiotarsus
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_tibiotarsus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:Tibiotarsus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_tibiotarsus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_tibiotarsus)


# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:Tibiotarsus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_tibiotarsus))
print(paste("AIC of Current Model:", aic_m3))


# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_tibiotarsus < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_tibiotarsus
  all_terms <- setdiff(all_terms, "TotalLength:Tibiotarsus")
  print("TotalLength:Tibiotarsus is included in the model.")
} else {
  print("TotalLength:Tibiotarsus is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, TotalLength:SkullWidth 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_skullWidth <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:SkullWidth, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_skullWidth <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_skullWidth)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:SkullWidth:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_skullWidth))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_skullWidth < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_skullWidth
  all_terms <- setdiff(all_terms, "TotalLength:SkullWidth")
  print("TotalLength:SkullWidth is included in the model.")
} else {
  print("TotalLength:SkullWidth is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, TotalLength:Sternum 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_sternum <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:Sternum, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_sternum <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_sternum)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + TotalLength:Sternum:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_sternum))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_sternum < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_totalLength_sternum
  all_terms <- setdiff(all_terms, "TotalLength:Sternum")
  print("TotalLength:Sternum is included in the model.")
} else {
  print("TotalLength:Sternum is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, AlarExtent:Weight
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_weight <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + AlarExtent:Weight, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_weight <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_weight)


# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + AlarExtent:Weight:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_weight))
print(paste("AIC of Current Model:", aic_m3))


# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_weight < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_weight
  all_terms <- setdiff(all_terms, "AlarExtent:Weight")
  print("AlarExtent:Weight is included in the model.")
} else {
  print("AlarExtent:Weight is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, AlarExtent:BeakHead
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_beakHead <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + AlarExtent:BeakHead, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_beakHead <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_beakHead)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + AlarExtent:BeakHead:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_beakHead))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_beakHead < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_beakHead
  all_terms <- setdiff(all_terms, "AlarExtent:BeakHead")
  print("AlarExtent:BeakHead is included in the model.")
} else {
  print("AlarExtent:BeakHead is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, AlarExtent:Humerus 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_humerus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + AlarExtent:Humerus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_humerus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_humerus)


# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + AlarExtent:Humerus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_humerus))
print(paste("AIC of Current Model:", aic_m3))


# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_humerus < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_humerus
  all_terms <- setdiff(all_terms, "AlarExtent:Humerus")
  print("AlarExtent:Humerus is included in the model.")
} else {
  print("AlarExtent:Humerus is not included in the model.")
}

```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, AlarExtent:Femur 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_femur <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + AlarExtent:Femur, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_femur <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_femur)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + AlarExtent:Femur:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_femur))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_femur < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_femur
  all_terms <- setdiff(all_terms, "AlarExtent:Femur")
  print("AlarExtent:Femur is included in the model.")
} else {
  print("AlarExtent:Femur is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, AlarExtent:Tibiotarsus 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_tibiotarsus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + AlarExtent:Tibiotarsus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_tibiotarsus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_tibiotarsus)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + AlarExtent:Tibiotarsus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_tibiotarsus))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_tibiotarsus < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_tibiotarsus
  all_terms <- setdiff(all_terms, "AlarExtent:Tibiotarsus")
  print("AlarExtent:Tibiotarsus is included in the model.")
} else {
  print("AlarExtent:Tibiotarsus is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, AlarExtent:SkullWidth 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_skullWidth <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + AlarExtent:SkullWidth, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_skullWidth <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_skullWidth)


# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + AlarExtent:SkullWidth:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_skullWidth))
print(paste("AIC of Current Model:", aic_m3))


# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_skullWidth < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_skullWidth
  all_terms <- setdiff(all_terms, "AlarExtent:SkullWidth")
  print("AlarExtent:SkullWidth is included in the model.")
} else {
  print("AlarExtent:SkullWidth is not included in the model.")
}

```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, AlarExtent:Sternum 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_sternum <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + AlarExtent:Sternum, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_sternum <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_sternum)


# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + AlarExtent:Sternum:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_sternum))
print(paste("AIC of Current Model:", aic_m3))


# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_sternum < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_alarExtent_sternum
  all_terms <- setdiff(all_terms, "AlarExtent:Sternum")
  print("AlarExtent:Sternum is included in the model.")
} else {
  print("AlarExtent:Sternum is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Weight:BeakHead
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_beakHead <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Weight:BeakHead, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_beakHead <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_beakHead)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Weight:BeakHead:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_beakHead))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_beakHead < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_beakHead
  all_terms <- setdiff(all_terms, "Weight:BeakHead")
  print("Weight:BeakHead is included in the model.")
} else {
  print("Weight:BeakHead is not included in the model.")
}

```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Weight:Humerus
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_humerus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Weight:Humerus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_humerus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_humerus)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Weight:Humerus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_humerus))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_humerus < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_humerus
  all_terms <- setdiff(all_terms, "Weight:Humerus")
  print("Weight:Humerus is included in the model.")
} else {
  print("Weight:Humerus is not included in the model.")
}

```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Weight:Femur
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_femur <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Weight:Femur, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_femur <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_femur)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Weight:Femur:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_femur))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_femur < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_femur
  all_terms <- setdiff(all_terms, "Weight:Femur")
  print("Weight:Femur is included in the model.")
} else {
  print("Weight:Femur is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Weight:Tibiotarsus
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_tibiotarsus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Weight:Tibiotarsus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_tibiotarsus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_tibiotarsus)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Weight:Tibiotarsus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_tibiotarsus))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_tibiotarsus < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_tibiotarsus
  all_terms <- setdiff(all_terms, "Weight:Tibiotarsus")
  print("Weight:Tibiotarsus is included in the model.")
} else {
  print("Weight:Tibiotarsus is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Weight:SkullWidth
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_skullWidth <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Weight:SkullWidth, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_skullWidth <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_skullWidth)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Weight:SkullWidth:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_skullWidth))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_skullWidth < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_skullWidth
  all_terms <- setdiff(all_terms, "Weight:SkullWidth")
  print("Weight:SkullWidth is included in the model.")
} else {
  print("Weight:SkullWidth is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Weight:Sternum
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Weight:Sternum, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Weight:Sternum:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum
  all_terms <- setdiff(all_terms, "Weight:Sternum")
  print("Weight:Sternum is included in the model.")
} else {
  print("Weight:Sternum is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, BeakHead:Humerus
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_humerus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + BeakHead:Humerus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_humerus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_humerus)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + BeakHead:Humerus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_humerus))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_humerus < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_humerus
  all_terms <- setdiff(all_terms, "BeakHead:Humerus")
  print("BeakHead:Humerus is included in the model.")
} else {
  print("BeakHead:Humerus is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, BeakHead:Femur
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_femur <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + BeakHead:Femur, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_femur <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_femur)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + BeakHead:Femur:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_femur))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_femur < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_femur
  all_terms <- setdiff(all_terms, "BeakHead:Femur")
  print("BeakHead:Femur is included in the model.")
} else {
  print("BeakHead:Femur is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, BeakHead:Tibiotarsus
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_tibiotarsus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + BeakHead:Tibiotarsus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_tibiotarsus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_tibiotarsus)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + BeakHead:Tibiotarsus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_tibiotarsus))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_tibiotarsus < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_tibiotarsus
  all_terms <- setdiff(all_terms, "BeakHead:Tibiotarsus")
  print("BeakHead:Tibiotarsus is included in the model.")
} else {
  print("BeakHead:Tibiotarsus is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, BeakHead:SkullWidth
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_skullWidth <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + BeakHead:SkullWidth, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_skullWidth <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_skullWidth)


# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + BeakHead:SkullWidth:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_skullWidth))
print(paste("AIC of Current Model:", aic_m3))


# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_skullWidth < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_skullWidth
  all_terms <- setdiff(all_terms, "BeakHead:SkullWidth")
  print("BeakHead:SkullWidth is included in the model.")
} else {
  print("BeakHead:SkullWidth is not included in the model.")
}

```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, BeakHead:Sternum
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_sternum <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + BeakHead:Sternum, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_sternum <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_sternum)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + BeakHead:Sternum:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_sternum))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_sternum < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_beakHead_sternum
  all_terms <- setdiff(all_terms, "BeakHead:Sternum")
  print("BeakHead:Sternum is included in the model.")
} else {
  print("BeakHead:Sternum is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Humerus:Femur 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur + Humerus:Femur, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Humerus:Femur:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur
  all_terms <- setdiff(all_terms, "Humerus:Femur")
  print("Humerus:Femur is included in the model.")
} else {
  print("Humerus:Femur is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Humerus:Tibiotarsus 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_tibiotarsus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Humerus:Tibiotarsus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_tibiotarsus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_tibiotarsus)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Humerus:Tibiotarsus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_tibiotarsus))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_tibiotarsus < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_tibiotarsus
  all_terms <- setdiff(all_terms, "Humerus:Tibiotarsus")
  print("Humerus:Tibiotarsus is included in the model.")
} else {
  print("Humerus:Tibiotarsus is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Humerus:SkullWidth 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_skullWidth <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Humerus:SkullWidth, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_skullWidth <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_skullWidth)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Humerus:SkullWidth:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_skullWidth))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_skullWidth < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_skullWidth
  all_terms <- setdiff(all_terms, "Humerus:SkullWidth")
  print("Humerus:SkullWidth is included in the model.")
} else {
  print("Humerus:SkullWidth is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Humerus:Sternum 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_sternum <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Humerus:Sternum, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_sternum <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_sternum)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Humerus:Sternum:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_sternum))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_sternum < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_sternum
  all_terms <- setdiff(all_terms, "Humerus:Sternum")
  print("Humerus:Sternum is included in the model.")
} else {
  print("Humerus:Sternum is not included in the model.")
}

```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Femur:Tibiotarsus
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_tibiotarsus <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur + Humerus:Femur + Femur:Tibiotarsus, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_tibiotarsus <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_tibiotarsus)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur + Humerus:Femur + Femur:Tibiotarsus:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_tibiotarsus))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_tibiotarsus < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_tibiotarsus
  all_terms <- setdiff(all_terms, "Femur:Tibiotarsus")
  print("Femur:Tibiotarsus is included in the model.")
} else {
  print("Femur:Tibiotarsus is not included in the model.")
}

```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Femur:SkullWidth
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_skullWidth <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur + Humerus:Femur + Femur:SkullWidth, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_skullWidth <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_skullWidth)


# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur + Humerus:Femur + Femur:SkullWidth:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_skullWidth))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_skullWidth < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_skullWidth
  all_terms <- setdiff(all_terms, "Femur:SkullWidth")
  print("Femur:SkullWidth is included in the model.")
} else {
  print("Femur:SkullWidth is not included in the model.")
}

```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Femur:Sternum
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_sternum <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur + Humerus:Femur + Femur:Sternum, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_sternum <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_sternum)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur + Humerus:Femur + Femur:Sternum:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_sternum))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_sternum < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_femur_sternum
  all_terms <- setdiff(all_terms, "Femur:Sternum")
  print("Femur:Sternum is included in the model.")
} else {
  print("Femur:Sternum is not included in the model.")
}

```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Tibiotarsus: SkullWidth 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_tibiotarsus_skullWidth <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur + Humerus:Femur + Tibiotarsus:SkullWidth, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_tibiotarsus_skullWidth <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_tibiotarsus_skullWidth)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur + Humerus:Femur + Tibiotarsus:SkullWidth:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_tibiotarsus_skullWidth))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_tibiotarsus_skullWidth < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_tibiotarsus_skullWidth
  all_terms <- setdiff(all_terms, "Tibiotarsus:SkullWidth")
  print("Tibiotarsus:SkullWidth is included in the model.")
} else {
  print("Tibiotarsus:SkullWidth is not included in the model.")
}

```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, Tibiotarsus: Sternum 
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_tibiotarsus_sternum <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur + Humerus:Femur + Tibiotarsus:Sternum, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_tibiotarsus_sternum <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_tibiotarsus_sternum)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur + Humerus:Femur + Tibiotarsus:Sternum:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_tibiotarsus_sternum))
print(paste("AIC of Current Model:", aic_m3))


# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_tibiotarsus_sternum < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_humerus_femur_sex_totalLength_sex_alarExtent_sex_femur_tibiotarsus_sternum
  all_terms <- setdiff(all_terms, "Tibiotarsus:Sternum")
  print("Tibiotarsus:Sternum is included in the model.")
} else {
  print("Tibiotarsus:Sternum is not included in the model.")
}
```
```{r}
# Sex, TotalLength, AlarExtent, Weight, BeakHead, Humerus, Sternum, Sex:TotalLength, Sex:AlarExtent, SkullWidth:Sternum
model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_skullWidth_sternum <- glm(Survival ~ Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur + Humerus:Femur + SkullWidth:Sternum, data = bump, family = binomial(link = logit))
aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_skullWidth_sternum <- AIC(model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_skullWidth_sternum)

# Compare AIC Values
aic_m3 <- AIC(m3)
print(paste("AIC with Sex + TotalLength + AlarExtent + Weight + BeakHead + Humerus + Sternum + Sex:TotalLength + Sex:AlarExtent + Sex:Femur + Humerus:Femur + SkullWidth:Sternum:", aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_skullWidth_sternum))
print(paste("AIC of Current Model:", aic_m3))

# Decide 
if (aic_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_skullWidth_sternum < aic_m3) {
  m3 <- model_with_sex_totalLength_alarExtent_weight_beakHead_humerus_sternum_sex_totalLength_sex_alarExtent_weight_sternum_humerus_femur_skullWidth_sternum
  all_terms <- setdiff(all_terms, "SkullWidth:Sternum")
  print("SkullWidth:Sternum is included in the model.")
} else {
  print("SkullWidth:Sternum is not included in the model.")
}
```
```{r}
summary(m3)
```

Forward Selection for Main effects and interaction terms (STEPAIC)
```{r}
# Initialize and Define Variables
null_model <- glm(Survival ~ 1, data = bump, family = binomial(link = logit))
m4 <- null_model
main_effects <- c("Sex", "TotalLength", "AlarExtent", "Weight", "BeakHead", "Humerus", "Femur", "Tibiotarsus", "SkullWidth", "Sternum")
interaction_terms <- c()

# Create interaction terms
for (i in main_effects) {
  for (j in setdiff(main_effects, i)) {
    interaction_terms <- c(interaction_terms, paste(i, j, sep = ":"))
  }
}

# Include both main effects and interaction terms in the initial set
all_terms <- c(main_effects, interaction_terms)

# Forward Selection 
while (length(all_terms) > 0) {
  aic_values <- numeric(length(all_terms))
  models <- vector("list", length(all_terms))
  
  for (term_index in seq_along(all_terms)) {
    term <- all_terms[term_index]
    formula_string <- paste("Survival ~", paste(c(attr(current_model$terms, "term.labels"), term), collapse = " + "))
    
    # Attempt to fit the model and check for errors
    candidate_model <- try(glm(as.formula(formula_string), data = bump, family = binomial(link = logit)), silent = TRUE)
    
    if (inherits(candidate_model, "try-error")) {
      next  # Skip to the next iteration if there's an error
    }
    
    # Store AIC and the model
    aic_values[term_index] <- AIC(candidate_model)
    models[[term_index]] <- candidate_model
  }
  
  # Skip if all models resulted in an error
  if (all(is.na(aic_values))) {
    break
  }
  
  # Find the model with the smallest AIC value
  min_index <- which.min(aic_values)
  min_aic <- aic_values[min_index]
  
  # Check if the smallest AIC value is less than the AIC of the current model
  if (min_aic < AIC(current_model)) {
    m4 <- models[[min_index]]
    all_terms <- setdiff(all_terms, all_terms[min_index])
  } else {
    break
  }
}

summary(m4)
```

Drop in deviance goodness-of-fit test for nested model
```{r}
anova(currentmodel, m3, test = "Chisq")
```
We perform a chi-square test to determine if the more complex model with additional predictors (m3) significantly improves the fit compared to the first model, `currentmodel`.

Given the p-value of 0.1903, there isn't a statistically significant difference in the fit of the two models at the 0.05 significance level. This suggests that adding the interaction terms in the first model does not provide a statistically significant improvement in fit over m3. Therefore, we choose `currentmodel` for its simplicity, as the more complex model does not offer a significantly better explanation of the data.


Odds of survival given `TotalLength`
```{r}
summary(currentmodel)

min(bump$TotalLength)
max(bump$TotalLength)

# Calculate the odds for lower quartile of total length 
odds_lower <- exp(17.4548 -0.4179 * (152))

# Calculate the odds for upper quartile of total length 
odds_upper <- exp(17.4548 -0.4179 * (167))

# Calculate the odds ratio
odds_ratio <- odds_upper / odds_lower

# Calculate the percentage change
percentage_change <- (odds_ratio - 1) * 100

# Print the results
cat("Odds of Survival for lower quartile:", odds_lower, "\n")
cat("Odds of Survival for upper quartile:", odds_upper, "\n")
cat("Odds Ratio (lower vs. upper):", odds_ratio, "\n")
cat("Percentage Change:", percentage_change, "%\n")

# Calculates the multiplicative change in odds for a one-unit increase in Total Length
exp(-0.4179)
```
1. In `currentmodel`, the coefficient for TotalLength is -0.4179. This suggests that for every one-unit increase in TotalLength, the log-odds of survival decrease by -0.4179.

2. We calculate the odds of survival for the lower and upper quartiles of `Total Length`. The result of the lower quartile is 9.858036e-21, indicating very low odds. While the result of the upper quartile is 1.868166e-23, even lower than the lower quartile.

3. The odds ratio is 0.001895069, which indicates the odds of survival at the upper quartile are much lower compared to the lower quartile. The percentage change of -99.81049% indicates a drastic decrease in survival odds from the lower to the upper quartile of `TotalLength`. 

4. The value 0.6584281 suggests that for every unit increase in `TotalLength`, the odds of survival decrease by approximately 34%. 

Confidence Interval for `TotalLength`
```{r}
ci <- c(-0.4179 - 1.96 * 0.1014, -0.4179 + 1.96 * 0.1014)
ci
```
We perform a confidence interval to provide an estimate of the range within which the regression coefficient is likely to fall. A narrower interval suggests a more precise estimate, while a wider interval indicates less precision.

The output -0.616644 -0.219156 represents the lower and upper bounds of the 95% confidence interval for the coefficent of `TotalLength`.
The results suggest that we can be 95% confident that the true value of the `TotalLength` coefficient lies between -0.975468 and -0.325532. Since the entire confidence interval is below zero, it suggests that the relationship between `Total Length` and the log odds of survival of a sparrow is significantly negative. An increase in `Total Length` is associated with a decrease in the log odds of survival.
The fact that zero is not included in this interval indicates that the effect of Total Length is statistically significant at the 5% significance level.

Odds of survival given `Humerus`
```{r}
summary(currentmodel)

min(bump$Humerus)
max(bump$Humerus)

# Calculate the odds for lower quartile 
odds_lower <- exp(17.4548 +51.4046 * (.659))

# Calculate the odds for upper quartile 
odds_upper <- exp(17.4548 +51.4046 * (.78))

# Calculate the odds ratio
odds_ratio <- odds_upper / odds_lower

# Calculate the percentage change
percentage_change <- (odds_ratio - 1) * 100

# Print the results
cat("Odds of Survival for lower quartile:", odds_lower, "\n")
cat("Odds of Survival for upper quartile:", odds_upper, "\n")
cat("Odds Ratio (lower vs. upper):", odds_ratio, "\n")
cat("Percentage Change:", percentage_change, "%\n")

# Calculates the multiplicative change in odds for a one-unit increase in predictor
exp(51.4046)
```
1. The coefficient for Humerus suggests that for every one-unit increase in the humerus, the log-odds of survival increase by 51.4046. The large increase indicates a strong positive association between humerus size and the log-odds of survival. 

2. We calculate the odds of survival for the lower and upper quartiles of `Humerus`. The result of the lower quartile is 1.961206e+22, indicating very high odds of survival. While the result of the upper quartile is 9.858616e+24, even larger than the lower quartile, suggesting even higher odds of survival.

3. The odds ratio is 502.6814, which indicates the odds of survival at the upper quartile of Humerus size is approximately 503 times higher than the lower quartile. While the percentage change of 50168.14% represents a massive increase in survival odds from the lower to the upper quartile of `Humerus`. 

4. The value 2.112196e+22 suggests that for every unit increase in `Humerus`, the odds of survival increase by a factor of 2.112196e+22. 

Confidence Interval for `Humerus`
```{r}
ci <- c(51.4046 - 1.96 * 14.8298, 51.4046 + 1.96 * 14.8298)
ci
```
The output 22.33819 80.47101 represents the lower and upper bounds of the 95% confidence interval for the coefficent of `Humerus`. The results indicate a wide range, which suggests the presence of uncertainty in the exact size; however, consistently suggests a positive relationship. 
Since the entire confidence interval is above zero, it suggests that the relationship between `Humerus` and the log odds of survival of a sparrow is significantly positive. This means that an increase in the size of Humerus is associated with an increase in the log odds of survival.
The fact that zero is not included in this interval indicates that the effect of Total Length is statistically significant at the 5% significance level.

Odds of survival given `Sex`
```{r}
summary(currentmodel)

# Calculate the odds for females 
odds_lower <- exp(17.4548 -1.5958 * (1))

# Calculate the odds for males
odds_upper <- exp(17.4548 -1.5958 * (0))

# Calculate the odds ratio
odds_ratio <- odds_upper / odds_lower

# Calculate the percentage change
percentage_change <- (odds_ratio - 1) * 100

# Print the results
cat("Odds of Survival for lower quartile:", odds_lower, "\n")
cat("Odds of Survival for upper quartile:", odds_upper, "\n")
cat("Odds Ratio (lower vs. upper):", odds_ratio, "\n")
cat("Percentage Change:", percentage_change, "%\n")

# Calculates the multiplicative change in odds for a one-unit increase in predictor
exp(-1.5958)
```
Note: The baseline group for the variable `Sex` in this analysis is for males, coded 0. Therefore, the coefficient in the regression analysis pertains to the change in log-odds survival of females. 

1. The coefficient for `Sex` suggests that for every female sparrow, the log-odds of survival decreases by 1.5958. This indicates a negative association between the `Sex` variable and the log-odds of survival of a female sparrow.  

2. The calculated odds of survival for females is 7717492. While the calculated odds for males are even higher at 38064780. This suggests that male sparrows has an even higher odds of survival.

3. The odds ratio of 4.932273 indicates that male sparrows has about 4.93 times higher odds of survival than female sparrows. In addition, the percentage change of 393.2273% suggests a significant difference in survival odds between the two groups.

4. The value 0.2027463 suggests that for every sparrow that is female, the odds of survival decrease by approximately 80%.

```{r}
ci <- c(-1.5958 - 1.96 * 0.5282, -1.5958 + 1.96 * 0.5282)
ci
```
The output -2.631072 -0.560528 represents the lower and upper bounds for the coefficent of `Sex`. 
Since the entire confidence interval is below zero, it reinforces the negative relationship between a female sparrow and the log odds of survival. This means that as `Sex` increases (from 0 to 1), the odds of survival decrease. The exclusion of zero from this interval indicates that the effect of `Sex` on survival is statistically significant at the 5% significance level.

Odds of survival given `Weight`
```{r}
summary(currentmodel)
min(bump$Weight)
max(bump$Weight)

# Calculate the odds for lower quartile 
odds_lower <- exp(17.4548 -0.8259 * (22.6))

# Calculate the odds for upper quartile
odds_upper <- exp(17.4548 -0.8259 * (31))

# Calculate the odds ratio
odds_ratio <- odds_upper / odds_lower

# Calculate the percentage change
percentage_change <- (odds_ratio - 1) * 100

# Print the results
cat("Odds of Survival for lower quartile:", odds_lower, "\n")
cat("Odds of Survival for upper quartile:", odds_upper, "\n")
cat("Odds Ratio (lower vs. upper):", odds_ratio, "\n")
cat("Percentage Change:", percentage_change, "%\n")

# Calculates the multiplicative change in odds for a one-unit increase in predictor
exp(-0.8259)
```

1. The coefficient for `Weight` suggests that for every unit increase in weight, the log-odds of survival decreases by 0.8259. This indicates a negative association between the variable `Weight` and the log-odds of survival.  

2. We calculate the odds of survival for the lower and upper quartiles of `Weight`. The result of the lower quartile is 0.2980363, which suggest that at the lower quartile of weight, the odds of survival is relatively higher. While the result of the upper quartile at 0.0002892845, is significantly lower. This suggests that at the upper quartile, the odds of survival are much lower. 

3. The odds ratio of 0.0009706351 indicates thatthe odds of survival at the upper quartile of `Weight` are much lower than at the lower quartile. In addition, the percentage change of -99.90294% suggests a significant decrease in survival odds from the lower to the upper quartile of `Weight`.

4. The value 0.4378408 suggests that for every increase in a sparrows weight, the odds of survival decreases by approximately 57%.

```{r}
ci <- c(-0.8259 - 1.96 *0.2348, -0.8259 + 1.96 *0.2348)
ci
```
The output -1.286108, -0.365692 represents the lower and upper bounds for the coefficent of `Weight`. 
Since the entire confidence interval is below zero, it reinforces the negative relationship between `Weight` and the log-odds of survival. This means that an increase in `Weight` is associated with a decrease in the log odds of survival. The exclusion of zero from this interval indicates that the effect of weight on survival is statistically significant at the 5% significance level.

Odds of survival given `Sternum`
```{r}
summary(currentmodel)
min(bump$Sternum)
max(bump$Sternum)

# Calculate the odds for lower quartile 
odds_lower <- exp(17.4548 + 16.8185 * (0.734))

# Calculate the odds for upper quartile
odds_upper <- exp(17.4548 + 16.8185 * (0.927))


# Calculate the odds ratio
odds_ratio <- odds_upper / odds_lower

# Calculate the percentage change
percentage_change <- (odds_ratio - 1) * 100

# Print the results
cat("Odds of Survival for lower quartile:", odds_lower, "\n")
cat("Odds of Survival for upper quartile:", odds_upper, "\n")
cat("Odds Ratio (lower vs. upper):", odds_ratio, "\n")
cat("Percentage Change:", percentage_change, "%\n")

# Calculates the multiplicative change in odds for a one-unit increase in predictor
exp(16.8185)
```

1. The coefficient for `Sternum` suggests that for every unit increase in the size of a sparrow's sternum, the log-odds of survival increases by 16.8185. This indicates a positive association between the variable `Sternum` and the log-odds of survival.  

2. We calculate the odds of survival for the lower and upper quartiles of `Sternum`. The result of the lower quartile is 8.745663e+12. The very large number suggests extremely high odds of survival at the lower quartile of `Sternum`. While the result of the upper quartile at 2.246466e+14, is even larger than the lower quartile, indicating even higher odds of survival.

3. The odds ratio of 25.68663 indicates that the odds of survival at the upper quartile of `Sternum` are approximately 25.69 times higher than at the lower quartile. In addition, the percentage change of 2468.663% suggests a significant increase in survival odds from the lower to the upper quartile of `Sternum`.

4. The very large value of `exp(16.8185)`, indicates how much the odds of survival are expected to increase with each additional unit increase in Sternum size. The resulting value of 20145671 suggests that even a small increase in the size of a sparrows sternum significantly increases the odds of survival.

```{r}
ci <- c(16.8185 - 1.96 *8.1808, 16.8185 + 1.96 *8.1808)
ci
```
The output 0.784132 32.852868 represents the lower and upper bounds for the coefficent of `Sternum`. 
Since the entire confidence interval is above zero, it reinforces the strong positive relationship between Sternum size and the log-odds of survival. This means that an increase in `Sternum` is associated with an increase in the log odds of survival. The exclusion of zero from this interval indicates that the effect of sternum on survival is statistically significant at the 5% significance level.


